Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-10-19 MCQMC2022ChallengesQMCSoftwareArticle_revision_2_toeditors.tex
Fred 2023 Mac 14 Updates

%\input FJHDef.tex
\newcommand{\AGSComment}[1]{{\color{red} #1}}
\newcommand{\FredComment}[1]{{\color{blue} Fred: #1}}
\newcommand{\SCComment}[1]{{\color{green} Sou-Cheng: #1}}
\newcommand{\YDComment}[1]{{\color{orange} Yuhan: #1}}
\newcommand{\JagsComment}[1]{{\color{violet} Jags: #1}}
\newcommand{\LSComment}[1]{{\color{blue} Linus Seelinger: #1}}
\DeclareMathOperator{\disc}{disc}
\newcommand{\FJHNote}[1]{{\color{blue}Fred: #1}}

@@

A QMC approximation of $\mu := \EE[f(\bsX)]$, $\bsX \sim \calU[0,1]^d$ can be implemented in a few steps:
\begin{enumerate}
    \item Draw a sequence of $n$ low discrepancy (LD) \cite{Nie92, SloJoe94, DicEtal14a, DicEtal22a} nodes,
    $\bsx_1,\dots,\bsx_n$ that mimic $\calU[0,1]^d$.
    \item Evaluate the integrand $f$ at these nodes to obtain $f(\bsx_i)$, $i=1,\dots,n$.
    \item Estimate the true mean, $\mu$, by the sample mean,
    \begin{equation}
        \hat{\mu}_n := \frac{1}{n} \sum_{i=1}^n f(\bsx_i).
        \label{eq:mc_average}
    \end{equation}
\end{enumerate}

@@

Expanding on the problem formulation in the introduction, we want to approximate well the integral or expectation, $\mu$, by the sample mean, $\hat{\mu}_n$:
\begin{gather}
\label{eq:cubSummary}
	\mu : = \int_\calT g(\bst) \, \lambda(\bst) \, \D \bst  = \bbE[f(\bsX)] = \int_{[0,1]^d} f(\bsx)  \, \D \bsx \approx \frac 1n \sum_{i=1}^{n} f(\bsx_i) =: \hat{\mu}_n, \\
 \label{CDHJS_eq:error_tol}
 \abs{\mu - \hat{\mu}_n} \le \varepsilon.
\end{gather}
Progressing from the original problem to a satisfactory solution requires several software components, which we describe in the subsections below.  Great QMC software environments allow different implementations of these components to be freely interchanged.

@@

\subsection{Integrands and Variable Transformations} \label{CDHJS:sec:integrands}
The original integral or expectation arising from an application is defined in terms of the integrand, $g :\mathcal{T} \to \R$, and the non-negative weight, $\lambda$, as described in \eqref{eq:cubSummary}.  For example,
\begin{itemize}
	\item $g$ is the discounted payoff of a financial derivative and $\lambda$ is the probability density function (PDF) for a discretized Brownian motion \cite{Gla03},

>>>>

%\input FJHDef.tex
%\newcommand{\AGSComment}[1]{{\color{red} #1}}
%\newcommand{\FredComment}[1]{{\color{blue} Fred: #1}}
%\newcommand{\SCComment}[1]{{\color{green} Sou-Cheng: #1}}
%\newcommand{\YDComment}[1]{{\color{orange} Yuhan: #1}}
%\newcommand{\JagsComment}[1]{{\color{violet} Jags: #1}}
%\newcommand{\LSComment}[1]{{\color{blue} Linus Seelinger: #1}}
%\DeclareMathOperator{\disc}{disc}
%\newcommand{\FJHNote}[1]{{\color{blue}Fred: #1}}

@@

A QMC approximation of $\mu := \EE[f(\bsX)]$, $\bsX \sim \calU[0,1]^d$ can be implemented in a few steps:
\begin{enumerate}
    \item Draw a sequence of $n$ low discrepancy (LD) \cite{Nie92, SloJoe94, DicEtal14a, DicEtal22a} nodes,
    $\bsx_1,\dots,\bsx_n$ that mimic $\calU[0,1]^d$.
    \item Evaluate the integrand $f$ at these nodes to obtain $f(\bsx_i)$, $i=1,\dots,n$.
    \item Estimate the true mean, $\mu$, by the sample mean,
    \begin{equation*}
        \hat{\mu}_n := \frac{1}{n} \sum_{i=1}^n f(\bsx_i).
        %\label{CDHJSeq:mc_average}
    \end{equation*}
\end{enumerate}

@@

Expanding on the problem formulation in the introduction, we want to approximate well the integral or expectation, $\mu$, by the sample mean, $\hat{\mu}_n$:
\begin{gather}
\label{CDHJSeq:cubSummary}
	\mu : = \int_\calT g(\bst) \, \lambda(\bst) \, \D \bst  = \bbE[f(\bsX)] = \int_{[0,1]^d} f(\bsx)  \, \D \bsx \approx \frac 1n \sum_{i=1}^{n} f(\bsx_i) =: \hat{\mu}_n, \\
 \label{CDHJS_eq:error_tol}
 \abs{\mu - \hat{\mu}_n} \le \varepsilon.
\end{gather}
Progressing from the original problem to a satisfactory solution requires several software components, which we describe in the subsections below.  Great QMC software environments allow different implementations of these components to be freely interchanged.

@@

\subsection{Integrands and Variable Transformations} \label{CDHJS:sec:integrands}
The original integral or expectation arising from an application is defined in terms of the integrand, $g :\mathcal{T} \to \R$, and the non-negative weight, $\lambda$, as described in \eqref{CDHJSeq:cubSummary}.  For example,
\begin{itemize}
	\item $g$ is the discounted payoff of a financial derivative and $\lambda$ is the probability density function (PDF) for a discretized Brownian motion \cite{Gla03},
